---
title: "simpleRegress"
author: "Karen Hernandez"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

```{r}
chest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chest)
summary.lm(chest)
```
According to the plot, we can see that LENGHT and CHEST the R- squared is 0.7869, just slightly bigger than LENGHT and NECK. 

```{r}
HEADLEN <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(HEADLEN)
summary.lm(HEADLEN)
```


We can see the linear models that headlen is a much better model because the adjusted r - squared 0.8434 which is bigger than the neck adjusted r squared 0.7476

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
pairs (bears)
```

A better approach as opposed to LENGTH and NECK is to use LENGH and HEADLEN because it has a larger adjusted R squared. The R squared value for LENGTH and NECK was 0.7476, the adjusted R squared value for LENGTH and HEADLEN was 0.8434.
